Proposed Solution

### 2017-04-15 PLDI/secs/concl.tex
fix typos

In this paper, we introduce \app, a highly modular framework 
that allows automatic verification of configuration files.
The main problem for verification of configuration files is their lack
of specification, so they are not a traditional target area
for formal methods.
Inspired by the association rule learning algorithm, \app learns 
a set of rules which describe properties and relations between keywords appearing in configuration files. These rules corresponding to the specification.
Our evaluation, based on a real-world  examples, shows that \app is able to
correctly detect and report configuration errors
including ordering, missing entry, integer correlation
and type errors.

>>>>

In this paper, we introduce \app, a highly modular framework 
that allows automatic verification of configuration files.
The main problem for verification of configuration files is their lack
of specification, so they are not a traditional target area
for formal methods.
Inspired by the association rule learning algorithm, \app learns 
a set of rules which describe properties and relations between keywords appearing in configuration files. These rules corresponding to the specification.
Our evaluation, based on a real-world  examples, shows that \app is able to
correctly detect and report configuration errors
including ordering, missing entry, integer correlation,
and type errors.

### 2017-04-15 PLDI/secs/eval.tex
fix words
fix typos

We have implemented a tool, \app, and evaluated it based on real-world configuration files taken from Github.
\app is written in Haskell and is available open source at \textit{url redacted for anonymity}.
Thanks to the Haskell's powerful type system, the implementation can easily be extended with with new rule classes or applied to different configuration languages with minimal change to the rest of the code base.
A user only needs to provide the functions for the rule interface (a typeclass in Haskell) to 1) learn relations from a single file 2) merge two sets of rules and 3) check a file given some set of rules.

@@

To evaluate our \app prototype, we require a separate training set and test set. 
For our training set, \trainingSet, we use a preexisting set of 256 
industrial MySQL configuration files collected in previous configuration 
analysis work~\cite{configdataset}.
This is an unlabeled training set, though most of the files have some errors.
For our test set, we collected 1000 MySQL configuration files 
from Github, and filtered the incorrectly formatted files out for a final 
total of 973 files.
In our evaluation we focus on MySQL for comparability of results, but \app can handle any configuration language (that can be parsed to the intermediate representation from Sec.~\ref{sec:trans}).

We report the number of rules learned from the training set and number of errors detected in the test set in Table~\ref{table:learning}.
One interesting note is that without probabilistic types we learned 327 fine grained rules and detected 1367 errors.
By introducing probabilistic types, we remove 114 rules and 1023 false positives.
We can be guaranteed these are all false positives since there cannot be a rule of type $size*size=size$ because of the semantic interpretation of the $size$ units.

@@

Although we cannot identify false positives, we can identify true positives by examining online forums, like StackOverflow, for record that
particular configuration settings have caused problems on real-world systems.
Furthermore, any error for which we can find evidence online is likely to be more problematic than errors that do not have an online record, 
  using the reasoning that this error has caused enough problems for people to seek help online.
In this case, we would like \app to can sort the errors by their importance or potential severity.
To achieve this sorting we use the rule graph analysis metric described in Sec.~\ref{sec:ruleorder}.

To estimate the impact of this metric, we track the rank of known true positives with, and without, the augmented rule ordering in Table~\ref{table-casestudy}.
For this table, we picked the known true positive rules, listed in the Errors column, and pick configuration files in the test set that have these errors.
We picked 3 files for each true positive by choosing the files the most total errors to most clearly observe the effects of our optimizations.
We test the following conditions; just rule graph analysis (RG) to sort the errors, just probabilistic types to filter the rules (PT), and both optimizations at the same time (RG $\land$ PT).
For each entry we list X/Y, where X is the rank of the known true positive, and Y is the total number of errors found on that file.

>>>>

We have implemented a tool, \app, and evaluated it based on real-world configuration files taken from Github.
\app is written in Haskell and is available open source at \textit{url redacted for anonymity}.
Thanks to the Haskell's powerful type system, the implementation can easily be extended with new rule classes or applied to different configuration languages with minimal change to the rest of the code base.
A user only needs to provide the functions for the rule interface (a typeclass in Haskell) to 1) learn relations from a single file 2) merge two sets of rules and 3) check a file given some set of rules.

@@

To evaluate our \app prototype, we require a separate training set and test set. 
For our training set, \trainingSet, we use a preexisting set of 256 
industrial MySQL configuration files collected in previous configuration 
analysis work~\cite{configdataset}.
This is an unlabeled training set, though most of the files have some errors.
For our test set, we collected 1000 MySQL configuration files 
from Github, and filtered the incorrectly formatted files out for a final 
total of 973 files.
In our evaluation, we focus on MySQL for comparability of results, but \app can handle any configuration language (that can be parsed to the intermediate representation from Sec.~\ref{sec:trans}).

We report the number of rules learned from the training set and the number of errors detected in the test set in Table~\ref{table:learning}.
One interesting note is that without probabilistic types we learned 327 fine grained rules and detected 1367 errors.
By introducing probabilistic types, we remove 114 rules and 1023 false positives.
We are guaranteed these are all false positives since there cannot be a rule of type $size*size=size$ because of the semantic interpretation of the $size$ units.

@@

Although we cannot identify false positives, we can identify true positives by examining online forums, like StackOverflow.
On these forums we find reports that particular configuration settings have caused problems on real-world systems.
Furthermore, any error for which we can find evidence online is likely to be more problematic than errors that do not have an online record, 
  using the reasoning that this error has caused enough problems for people to seek help online.
In this case, we would like \app to sort the errors by their importance or potential severity.
To achieve this sorting we use the rule graph analysis metric described in Sec.~\ref{sec:ruleorder}.

To estimate the impact of this metric, we track the rank of known true positives with, and without, the augmented rule ordering in Table~\ref{table-casestudy}.
For this table, we picked the known true positive rules, listed in the Errors column, and pick configuration files in the test set that have these errors.
We picked 3 files for each true positive by choosing the files with the highest number of total reported errors in order to clearly observe the effects of our optimizations.
Although this gives a more clear picture of the effect of our optimizations, it results in a slightly inflated false positive rate.

We test the following conditions; just rule graph analysis (RG) to sort the errors, just probabilistic types to filter the rules (PT), and both optimizations at the same time (RG $\land$ PT).
For each entry we list X/Y, where X is the rank of the known true positive, and Y is the total number of errors found in that file.

### 2017-04-15 PLDI/secs/motiv.tex
fix typos

%This example is a tricky configuration error, which implicitly
%includes a computational correlation among different entries
%in the configuration file.
We call these errors as {\em fine-grained integer correlations}. 
\app can also detect simpler integer correlation: one entry's
value should have a certain correlation with another entry's 
value.
For instance, in MySQL, the value of \code{key\_buffer} 
should be larger than \code{max\_allowed\_packet}.
While several existing tools~\cite{santolucitoCAV, zhang14encore}
can detect simple integer correlation errors,
\app is, to the best of our knowledge, the first system capable of
detecting such complex fine-grained integer correlation errors.

\para{Example~3: Type Errors} 
Many system availability problems are caused by 
assigning incorrect type of values. Consider the following  misconfiguration
file from github~\cite{typeerror}:
a user tries to install MySQL and she needs to initiate the path
of the log information generated by MySQL.
This user puts the following entry assignment in her MySQL
configuration file:

>>>>

%This example is a tricky configuration error, which implicitly
%includes a computational correlation among different entries
%in the configuration file.
We call these errors {\em fine-grained integer correlations}. 
\app can also detect simpler integer correlation: one entry's
value should have a certain correlation with another entry's 
value.
For instance, in MySQL, the value of \code{key\_buffer} 
should be larger than \code{max\_allowed\_packet}.
While several existing tools~\cite{santolucitoCAV, zhang14encore}
can detect simple integer correlation errors,
\app is, to the best of our knowledge, the first system capable of
detecting such complex fine-grained integer correlation errors.

\para{Example~3: Type Errors} 
Many system availability problems are caused by 
assigning incorrect values of an incorrect type to a keyword. Consider the following  misconfiguration
file from github~\cite{typeerror}:
a user tries to install MySQL and she needs to initiate the path
of the log information generated by MySQL.
This user puts the following entry assignment in her MySQL
configuration file:

### 2017-04-15 PLDI/secs/related.tex
fix typos

\para{Language-support misconfiguration checking}
There have been several language-support efforts proposed for preventing
configuration errors introduced by fundamental deficiencies in
either untyped or low-level languages. For example, in the network
configuration management area, administrators often
produce configuration errors in their routing configuration files.
PRESTO~\cite{enck07configuration} 
automates the generation of device-native configurations
with configlets in a template language. 
Loo {\em et al.}~\cite{loo05declarative} adopt Datalog to reason about 
routing protocols in a declarative fashion. 
COOLAID~\cite{chen10declarative} constructs
a language to describe domain knowledge about devices and
services for convenient network reasoning and management.
Compared with the above efforts, \app mainly focuses on software systems, 
\eg, MySQL and Apache, and our main purpose is to automate configuration
verification rather than proposing new languages 
to convenient configuration-file writing. 
The closest effort to \app is ConfigC~\cite{santolucitoCAV},
which aims to learn configuration-checking rules from a given training
set. Compared with \app, ConfigC has the following disadvantages.
First, ConfigC requires the configuration files in the training set must 
be correct, which is quite impractical, because it is very difficult to
determine a correct configuration set in reality.
Second, ConfigC can only cover less types of misconfigurations than \app. 
Finally, the training time of ConfigC is much longer than \app.

>>>>

\para{Language-support misconfiguration checking}
There have been several language-support efforts proposed for preventing
configuration errors introduced by fundamental deficiencies in
either untyped or low-level languages. For example, in the network
configuration management area, administrators often
produce configuration errors in their routing configuration files.
PRESTO~\cite{enck07configuration} 
automates the generation of device-native configurations
with configlets in a template language. 
Loo {\em et al.}~\cite{loo05declarative} adopt Datalog to reason about 
routing protocols in a declarative fashion. 
COOLAID~\cite{chen10declarative} constructs
a language to describe domain knowledge about devices and
services for convenient network reasoning and management.
Compared with the above efforts, \app mainly focuses on software systems, 
\eg, MySQL and Apache, and our main purpose is to automate configuration
verification rather than proposing new languages 
to convenient configuration-file writing. 
The closest effort to \app is ConfigC~\cite{santolucitoCAV},
which aims to learn configuration-checking rules from a given training
set. Compared with \app, ConfigC has the following disadvantages.
First, ConfigC requires the configuration files in the training set must 
be correct, which is impractical because it is very difficult to
determine a correct configuration set in reality.
Second, ConfigC covers fewer types of misconfigurations than \app. 
Finally, the training time of ConfigC is much longer than \app.
